Efficient implementation of penalized regression\\for genetic risk prediction

### 2019-01-31 paper/PRS-supp.tex
add table/figure

@@

>>>>

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{celiac-roc}}
\caption{ROC Curves for C+T-max, PLR and PLR3 for the celiac disease dataset. Models were trained using 12,000 individuals. These are results projecting these models on the remaining 3155 individuals. The figure is plotted using R package plotROC \cite[]{sachs2017plotroc}.\label{fig:celiac-roc}}
\end{figure}

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-lasso-path-height}}
\caption{Regularization path for `K = 10' validation sets when fitting our L1-penalized linear regression on 350,000 individuals of the UK Biobank. This plot can be obtained by using the `plot()' method on the object resulting from this fitting. This fitting used `nlambda = 200` and `n.abort = 10' (the defaults).}
\label{fig:supp-path}
\end{figure}
